After spending about a week reading through the SleekXMPP code we began to write
our own implementations of the Control and Sensor XEPs, so that we could compare
it against the SleekXMPP versions. Then we reviewed what parts of implementing
an XEP we needed to understand to begin developing Provisioning.

Before we began coding Provisioning we wrote our own IoT device and console to
exist as proof of concepts of how devices would interact over. The device would
implement a variety of features from Sensor and Control acting as a server (i.e.
not as an XMPP server, but as a device serving sensordata and controllable
fields that a client, in our context the console, would connect to and interact
with). Then we would implement our IoT console, which would act like an end user
application, sending sensordata requests and control commands to affect the
device. Once we had this implemented, we would develop the provisioning
component to then run a provisioning server with Prosody to handle Provisioning
protocol being sent between the IoT console and device.

However we ran into a snag. Once we got our device and console implemented we
were only receiving <service-unavailable> Iq errors. In this context, that meant
that when sending a sensordata request or control command were not listing that
those protocols were being supported in the discovery XEP 0030.

This lead us to believe that some of the features (i.e. a supported XEP/ XMPP
XML namespace)  were not being properly being added to the discovery plugin. We
checked, and as far as we could tell it was properly added. Then we decided to
run their existing discovery browser which gave us the same error but worked
with other common XMPP clients/accounts such as a gmail account logged in with
gchat.

So next we ran the requests locally such that a device would create its own
sensors and request them to itself. This gave us functional result but didn’t
clarify why it wasn’t working to other devices.

We used existing servers xmpp.jp \& darkdna.net, but this left us with
inconsistent results between these two servers; we eventually ran our own server
locally using the Prosody XMPP server.

Then we were finally able to get into contact with Lance (the current maintainer
of SleekXMPP) who was the person who committed Sensor and Control the SleekXMPP.
He was able to help us discover what our problem was. We doing a user error. The
method definition in python specified that the destination jid, source jid, and
asynchronous method callback be put in that order. However we put them in that
order with the pythons definition of position independent parameters (e.g.
request\_sensordata(from\_jid= ``jid1'', to\_jid= ``jid2'',
callback=req\_callback)
however it is just supposed to be in that order but without the positional
independent parameter definitions (e.g. request\_sensordata( ``jid1'',  ``jid2'',
req\_callback). This fixed our problem and allowed us to begin development on
Provisioning.

This, while a very simple developer error, eluded us for a variety of reasons.
When we had the initial parameter definitions, SleekXMPP appeared to be doing
what we thought it should be doing. We examined with debug messages and verified
the sent stanza was valid \texttt{request\_sensordata()}. However instead of SleekXMPP
throwing an error locally it sent the packet. Then sleek displayed that we
received an error packet from the device we were sending it to; although
examining the debug logs on the device side it didn’t specify that it was sent
by it. So we aren’t sure if something low level internal to sleekxmpp or the
servers we were using were spoofing a response to our sensordata request with an
error as if it was the device sending it itself.))
